The resevol package

### 2021-09-09 notebook/helicoverpa_notes.Rmd
More naming is switched over from helicoverpa to resevosevol

---
title: "The helicoverpa package"
author: "Brad Duthie and Rose McKeon"
output:
  html_document: default
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
linestretch: 1
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
bibliography: references.bib
---

>>>>

---
title: "The resevol package"
author: "Brad Duthie and Rose McKeon"
output:
  html_document: default
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
linestretch: 1
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
bibliography: references.bib
---

### 2021-09-09 notebook/index.Rmd
More naming is switched over from helicoverpa to resevosevol

> **This notebook tracks progress on the development of [helicoverpa](https://bradduthie.github.io/helicoverpa/) R package, a BBSRC [FAPESP Newton Funded](http://www.fapesp.br/en/9552) Project to model how the spatial scale of heterogeneity in fungal isolate application and crop plant cultivation affects variation in the selection landscape for biopesticide resistance.**

>>>>

> **This notebook tracks progress on the development of [resevol](https://bradduthie.github.io/resevol/) R package, a BBSRC [FAPESP Newton Funded](http://www.fapesp.br/en/9552) Project to model how the spatial scale of heterogeneity in fungal isolate application and crop plant cultivation affects variation in the selection landscape for biopesticide resistance.**
